% Jed Abanat Cover Letter - Cocoon Data
\documentclass[10pt,letterpaper]{article}

% Import configuration
\input{config/formatting}
\input{config/coverletter}

% Import resume sections
\begin{document}
\input{sections/header}

\vspace{30pt}

5 February 2024 \\ \\

Dear Hiring Manager, \\

I am writing to express my interest in the Senior Software Engineer role at Cocoon Data. As a software engineer with more than five years of experience in developing and maintaining complex applications, I am confident that I can bring significant value to the team. \\

Throughout my career at Fugro, I have consistently demonstrated my ability to independently manage and deliver high-quality and innovative software solutions. As the tech lead responsible for a lidar data processing solution (\href{https://www.youtube.com/watch?v=f65bdm4tous}{\underline{Fugro RAMMS}}), I have worked throughout the entire software development life cycle process from conceptualising and implementing prototypes, to comprehensive testing and deployment at a global scale. \\

Over the past five years I predominantly worked on desktop applications, where my responsibilities ranged from the research and development of low-level signal processing algorithms, to building high-performance data processing pipelines, and designing interactive user interfaces. I'm passionate about the user experience, and enjoyed the design and implementation of the UI, collaborating with the end-users to develop an intuitive and functional interface. \\

After resigning from my previous role at Fugro to travel and relocate back to Australia, I started working on enhancing my web-development skill set. A project I am particularly am proud of is {\underline{SkyTrace}} - my personal flight log application, that I built with NextJS. I was able to pick up TypeScript quickly and used Tailwind CSS, deploying the app on Vercel, with a PostgresSQL database. I also have some experience with AWS as I built a Wordpress blog site (running on a Lightsail instance, with content stored in S3). I am eager to bring these skills to Cocoon Data and confident in my ability to contribute to your client-facing website and platform. \\

I have firsthand experience with the challenges that Cocoon Data aims to solve, having previously encountered data sovereignty restrictions during my time at Fugro. While working on a project for the Florida Department of Environmental Protection, we had to redesign our data processing pipeline to comply with the data security requirements. The KBOSS \& SafeShare solutions offered by Cocoon Data are impressive as they address the complexities of secure data sharing, while remaining user-friendly and easily integrated into existing workflows. The "developer-first" mindset is apparent in how these solutions are built, and I can certainly see the business case for companies to adopt these solutions. \\

I grew up in Indonesia, following a home-schooling program until the age of 14 when I moved to Australia to complete my education. This fostered a strong sense of curiosity and initiative which were instrumental to my success at Fugro and led to the company sponsoring my relocation to Houston, Texas in 2019. I embraced a diverse range of responsibilities including acting as Agile Product Owner, developing data processing workflows, defining roadmaps, and providing ongoing support to the Operations team. I enjoyed this dynamic environment as juggling multiple responsibilities gave me a fuller perspective to contribute and shape the development of the product. \\

I’m drawn to this role at Cocoon Data because of your commitment to secure data solutions and the opportunity to work on projects with real impact. Thank you for considering my application. I look forward to discussing this opportunity further. \\

Sincerely,\\
Jed Abanat

\end{document}