\heading{Work Experience}

% Career break entry
\headerrow{\textbf{Career Break / Travel}}{\textit{July 2023 - Present}}
\vspace{-1.5em}

\workExperienceSubItem{
    \item Resigned to travel and relocate back to Australia. Available to start from February 2024.
}

\workExperienceItem
    {Fugro USA Marine}
    {Houston, TX, USA}
    {Innovation (Software) Engineer}
    {Sep 2019 - July 2023}

\workExperienceSubItem{
    \item Technical lead of a desktop software suite which processed airborne lidar bathymetry data. Wrote 70\% of the code and reviewed the remaining 30\%. Responsible for a team of 3 developers.
    \item \justifying{Developed a novel bathymetric lidar processing solution with the ML team to replace traditional signal processing algorithms with an image recognition approach. Resulted in 95\% less noise \& improved accuracy of final product by 30\%. Filed a patent for this invention - \textit{‘Machine Learning Processing of Airborne Lidar Bathymetric Waveform Data’}}
    \item \justifying{Architected and implemented a high-performance data processing pipeline using TPL Dataflow with a multi-process, event-driven approach achieving an 80\% reduction in processing time. Utilised Microsoft ONNX Runtime \& CUDA to run inference on the raw data with NVIDIA GPUs.}
    \item Refactored original MATLAB processing app into a .NET Core console app to improve code maintainability \& reliability, and facilitate future collaboration opportunities; emphasised on following SOLID principles \& implementing TDD which led to increased test coverage from 0\% to 85\%.
    \item \justifying{Effectively served as Agile Product Owner for 18 months, working with stakeholders to gather \& clarify requirements, prioritise deliverables, manage OKRs, \& define development roadmaps, ensuring alignment with business objectives.}
    \item Identified gaps within the Survey operations workflow; built 2 apps to support field staff - an automatic data transfer tool to copy the raw data (2TB/flight) \& a QC tool to generate georeferenced images collected during the flight.
    \item Implemented CI/CD pipelines in GitHub Actions to automate build \& testing, reducing release time by 2 hours.
    \item Rotated through two other teams and contributed to separate Windows application development; collaborated with architects to refactor legacy C\# code \& added functionality to encode/decode messages via TCP which allowed operators to remotely control winches. 
    \item \justifying{Contributed to a company-wide initiative to develop standardised Visual Studio .NET project configuration templates, improving developer experience and ensuring consistency across across all (50+) .NET repos.}
    \item Led code reviews and on-boarding programs to mentor colleagues, providing technical guidance and demonstrating best-practices. Presented at internal \textit{`Innovators Conference`} in 2020 \& 2022. 
}

\workExperienceItem
    {Fugro Australia Marine}
    {Adelaide, Australia}
    {Airborne Software Engineer}
    {Mar 2018 - Sep 2019}

\workExperienceSubItem{
    \item Maintained and improved an acquired MATLAB code-base as the sole developer, working autonomously to fix bugs and add additional features requested by data processors.
    \item Led fortnightly planning and demo meetings with global stakeholders to ensure alignment on key priorities and to collect feedback on new features \& bug fixes.
    \item Wrote Python scripts to produce ancillary Hydrographic data products, generating an additional \$8k per survey job.
    \item Researched, tested and developed signal processing \& noise filtering algorithms to improve peak detection accuracy.
    \item Travelled to Houston regularly to meet directly with end-users and external clients to gather requirements and collect app feedback. Provided hands-on field support and gained additional context to proactively identify and address bottlenecks (data storage management \& automating manual processes) in the processing workflow.
    \item Automated the deployment of the MATLAB code using Ruby scripts to compile and generate an installer.
    \item Developed comprehensive test procedure documents to compare the performance and accuracy of Fugro’s lidar sensors. Designed a rubric and scoring system for fair comparison between the sensors and provided recommendations to management for future development efforts.
    \item Designed mounting plates in AutoCAD to install lidar sensors in aircraft, adhering to all Civil Aviation Safety Authority (CASA) standard while ensuring mounting plate was adaptable to multiple aircraft.
}

\headerrow
{\emph{Engineering Intern}}
{\emph{Jan 2018 - Mar 2018}}
\vspace{-1em}
\workExperienceSubItem{
    \item Independently conducted thorough analysis of an acquired code-base in MATLAB ($\sim$8000 lines) to identify and understand each component and function of the process.
    \item Produced comprehensive technical documentation and detailed flowchart diagrams explaining the code to global stakeholders, resulting in improved cross-functional collaboration between the Adelaide \& Houston offices.
}
