\vspace{30pt}

26 February 2024 \\ \\

Dear Magda, \\

I am writing to express my interest in the Senior Software Engineer role at WiseTech. As a software engineer with more than five years of experience in developing and maintaining complex C\# applications, I am confident that I can bring significant value to the team. \\

Throughout my career at Fugro, I have consistently demonstrated my ability to independently manage and deliver high-quality and innovative software solutions. As the tech lead responsible for a lidar data processing solution (\href{https://www.youtube.com/watch?v=f65bdm4tous}{\underline{Fugro RAMMS}}), I have worked throughout the entire software development life cycle process from conceptualising and implementing prototypes, to comprehensive testing and deployment at a global scale. \\

I have extensive experience with C\# (.NET Core \& Framework) and have developed several console and GUI applications, following an Agile methodology to build highly-performant data processing pipelines with an emphasis on Test-Driven Development. I actively worked with end-users and global stakeholders to gather and understand their requirements, to then define the system's functionality and write a maintainable, highly testable, and robust application. As my domain knowledge grew, I was able to critically analyse and question proposed features to determine the actual need, and therefore the most effective solutions. \\

During the migration of the data processing application from MATLAB to C\#, I advocated for applying a TDD approach. The existing MATLAB app relied solely on user integration testing, which while functional, lacked the granularity of unit tests and only covered a small set of edge cases. I implemented additional logic to mitigate the risk from the edge cases that had previously been unaccounted for and to further minimise potential errors. As a result, we achieved a 85\% test coverage after the initial refactor (from 0\%) and were able to pay off a significant amount of tech-debt, ensuring a cleaner code base for future development and a more robust product for the end-users.\\

I grew up in Indonesia, following a home-schooling program until the age of 14 when I moved to Australia to complete my education. This fostered a strong sense of curiosity and initiative which were instrumental to my success at Fugro and led to the company sponsoring my relocation to Houston, Texas in 2019. I embraced a diverse range of responsibilities including acting as Agile Product Owner, developing data processing workflows, defining roadmaps, and providing ongoing support to the Operations team. I enjoyed this dynamic environment as juggling multiple responsibilities gave me a fuller perspective to contribute and shape the architecture of the product. \\

I’m drawn to this role at WiseTech because of the emphasis on continual improvement, not only with the solutions you build, but with the people and teams that work at WiseTech. Your value around developing customer-centric products that solve their real need is one that aligns closely with my own. I'm excited for the chance to experience your rotational program, to bring my skills and ideas to the team and work on meaningful projects. Thank you for considering my application. I look forward to discussing this opportunity further. \\

Sincerely,\\
Jed Abanat